---
title: "CEMA-sam.Rmd"
author: "SAMSON MWOLE"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 
```{r dataset}
 data <- read.csv("https://raw.githubusercontent.com/cema-uonbi/internship_task/main/data/cema_internship_task_2023.csv")
head(data,2)
```

## DATA ANALYSIS



```{r DATA}
colnames(data)
```

```{r dimension}
dim(data)# rows and  columnS
```

```{r ifMissing}
is.null(data)

```

## Checking for missing values in the dataframe


```{r sumMissing}
sum(is.na(data$Acute.Malnutrition ))#some missing null
```

 
# summary of the dataset
```{r summarry}
summary(data)#min mean median 1st and 3rd quartiles
```
 
# checking for outliers using a boxplot

```{r  outliers}
boxplot(data$diarrhoea.cases)#some outlier present
```

```{r  manipulate}
install.packages("tidyverse")
library(tidyverse)

aa <- data %>%
  group_by(county)  %>%
  summarise(avg_TotalDewormed_monthly = mean(Total.Dewormed	)) %>%
arrange(desc(avg_TotalDewormed_monthly))

aa
```


# Relationship between the 2
```{r  relationship}
library(ggplot2)

ggplot(data, aes(x=data$Acute.Malnutrition, y=data$Underweight.0..6.months)) +
  theme_bw() + 
  geom_jitter(alpha=0.25) + 
  geom_smooth() + 
  labs(x="Malnutrition", y="0-6 underweight")
```
# correlation between malnutrition and underweight

```{r  correlation}
res <- cor.test(data$Acute.Malnutrition, data$Underweight.0..6.months,                     method = "pearson")
res

```

# What is the average stunted growth in kitui county of kids between 0 and 6
```{r  kitui}
asb <- filter(data, county == "Kitui County")%>%
  summarise(avg_stunted = mean(stunted.0..6.months	))
  
asb
```


```{r   histogram }
hist(data$diarrhoea.cases)
```



# Correlation matrix
```{r    correlation map }
install.packages("lattice")
library(lattice)

tmp <- data %>% 
  dplyr::select( "Total.Dewormed" , "Acute.Malnutrition",       "stunted.6.23.months","stunted.0..6.months"   ,  
 "stunted.24.59.months", "diarrhoea.cases", "Underweight.0..6.months" , "Underweight.6.23.months" , "Underweight.24.59.Months")
head(tmp)
# rounding to 2 decimal places
corr_m <- round(cor(tmp),2) 
head(corr_m)  

# CORRELATION HEATMAP
install.packages("reshape2")
library(reshape2)
  
# reduce the size of correlation matrix
melted_corr_mat <- melt(corr_m)
# head(melted_corr_mat)

# section c questio 2 plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) +
  geom_tile()
```

# 2 sample t test to test for the difference in mean between stunted.0..6.months and stunted.24.59.months

```{r 2 sample t test }
t.test(data$stunted.0..6.months, data$stunted.24.59.months, var.equal = TRUE)
```
