---
title: "RMHI/ARMP Problem Set 2"
author: 'Your name and ID goes here [Word Count: XX]'
---

Please put your answers here, following the instructions in the assignment description. Put your answers and word count tallies in the locations indicated; if none is indicated that means there is no word count for that question. Remember to knit as you go, and submit the knitted version of this on Canvas.

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
# We'll begin by loading up the libraries and data we need, as always.
knitr::opts_chunk$set(echo = TRUE)

# loading the libraries
library(tidyverse)
library(here)
library(ggplot2)
library(lsr)
library(RColorBrewer)
library(car)

# loading datasets
do <- read_csv(file=here("others.csv"))
dl <- read_csv(file=here("liedetector.csv"))
dd <- read_csv(file=here("otherdata.csv"))
dd$size <- as.factor(dd$size)
ddt2 <- dd %>% filter(time=="t2")
```

## Q1 

```{r q1, warning=FALSE, message=FALSE, fig.width=3, fig.height=3}

# put your code here
#head(do, 5)
```

*ANSWER: Put your answer here. [Word count: XX]* 


## Q2 

```{r q2, warning=FALSE, message=FALSE, fig.width=4.7, fig.height=4}
# put your code here
# QUESTION 1 :A Pearson correlation test was used to test for the 
#correlation between height and scariness.
cor.test(do$height, do$scariness, 
                method = "pearson")

```


## Q3 

```{r q3, warning=FALSE, message=FALSE, fig.width=3, fig.height=3}
# put your code here
dd <- read_csv(file=here("otherdata.csv"))

head(dd,4)
t.test(dd$health ~ dd$time, var.equal = TRUE)
 
t.test(dd$health ~ dd$time, var.equal = TRUE)

#	Two Sample t-test

#data:  dd$health by dd$time
#t = 3.4088, df = 64, p-value = 0.001134
#alternative hypothesis: true difference in means between group t1 and group #t2 is not equal to 0
#95 percent confidence interval:
 # 3.988911 15.283816
#sample estimates:
#mean in group t1 mean in group t2 
 #       76.45455         66.81818 



#disabled <- dd[dd$disability == 'TRUE',]
#dim(disabled)
ddt2 <- dd %>% filter(time=="t2")
dim(ddt2)

t.test(ddt2$health ~ ddt2$size, var.equal = TRUE)
#oneway.test(health ~ size,
#+             data = ddt2,
#+             var.equal = TRUE)

#	One-way analysis of means

#data:  health and size
#F = 2.4855, num df = 2, denom df = 30, p-value = 0.1003

```

*ANSWER: Put your answer here. [Word count: XX]* 


## Q4

**Q4a**

```{r q4a, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
gfg_table =table(dd$time, dd$disability )
gfg_table
chisq.test(dd$time, dd$disability, correct=FALSE)
```

*ANSWER: Put your answer here. [Word count: XX]* 


**Q4b**

```{r q4b, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
anova(lm(health ~ size, data=ddt2))

```

*ANSWER: Put your answer here. [Word count: XX]* 

## Q5

```{r q5, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
fit <- lm(health ~ height, data = ddt2)
summary(fit)
```

*ANSWER: Put your answer here. [Word count: XX]* 


## Q6

*ANSWER: Put your answer here. [Word count: XX]* 


## Q7


```{r q7, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
dl <- read_csv(file=here("liedetector.csv"))
head(dl)
t.test(hr ~ type, data = dl)
```

*ANSWER: Assumption 1: Put your answer here. Assumption 2: Put your answer here [Word count: XX]* 


## Q8

```{r q8, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
# QUESTION 3: A two sided two sample t test was used to test for the difference in 
#the average of the heartbeat
head(dl)
t.test(hr ~ type, mu=0,alt="two.sided",data = dl)
```

*ANSWER: Put your answer here. [Word count: XX]* 

## Q9

**Q9a**

```{r q9a, warning=FALSE, message=FALSE, fig.width=3.5, fig.height=3}
# put your code here
#QUESTION TWO VISUALIZING THE BOXPLOT
library(ggplot2)
ggplot(data=dl,aes(x=name,y=hr,fill=type))+
  geom_boxplot()+
   ggtitle("Performance on lie detector test")+
  xlab("Name of the person")+
  ylab("Heart Rate")+
  geom_boxplot(trim=FALSE,,)+
  theme(
        legend.text = element_text(size = 6),
        legend.title = element_text(size=18,hjust = 0.5),
        legend.key.height = unit(1,"cm"),
        legend.key.width = unit(1,"cm"),
        legend.position=c(0.1,0.9))+
  guides(fill=guide_legend(title = "disp"))


```

 