# Team, insert the required components wherever indicated below on the raw, original version of this R codebook .Rmd file.

# TCP_R-MCIS6333_001

# Data Visualization Programming Team Course Project
# [INSERT YOUR USE CASE CLIET NAME]
# [INSERT YOUR USE CASE SUBJECT (this is either a product or service; for example: Food and Beverage Stands)]

# Created by:
# [INSERT YOUR TEAM #]
# [INSERT YOUR TEAM NAME]
# [INSERT FULL NAME OF TEAM MEMBER HERE]
# [INSERT FULL NAME OF TEAM MEMBER HERE]
# [INSERT FULL NAME OF TEAM MEMBER HERE]
# [IF YOU HAVE LESS THAN THREE TEAM MEMBERS, IT IS OKAY TO DELETE THE EXTRA NAME HOLDERS FROM ABOVE AND THIS LINE]

# Created for Dr. Esther Mead, SAU Fall 2023

# Created November 2, 2023

#========================SECTION SEPARATOR

# Student team, below this section, insert all code for data processing and data visualization (DV) that you used for any and all DVs that you created in R and inserted into your TCP OPR/PRES (you must have at least one R DV and no more than 9 R DVs).
# You must include all R code below that in necessary to recreate your DVs within the R web-based development environment (Posit Cloud RStudio Cloud): https://login.rstudio.cloud/login?redirect=%2F
# You must also insert optimized R code documentation lines throughout this notebook.
# Read the TCP Grading Rubric on Blackboard to prevent irreversible point penalties.
# Point penalties will be applied to all teams equally and are non-negotiable. All teams are treated equally.

#========================SECTION SEPARATOR

```{r }
library(readxl)
d1 <- read_excel("/datasets/10 - College Energy Drink - M1 - Initial dataset-2.xlsx")
d2 <- read_excel("/datasets/10 - College Energy Drink - M2 - Change Over Time-2.xlsx")
d3 <- read_excel("/datasets/10 - College Energy Drink - M3 - Data Composition-2.xlsx")
d4 <- read_excel("/datasets/10 - College Energy Drink - M4 - Data Distributions-1.xlsx")
d5 <- read_excel("/datasets/10 - College Energy Drink - M5 - Group Comparisons-1.xlsx")
d6 <- read_excel("/datasets/10 - College Energy Drink - M6 - Relationships.xlsx")
d7 <- read_excel("/datasets/10 - College Energy Drink - M7 - Geographical Data.xlsx")
```



```{r }
library(ggplot2)

head(d6, 4)
```


```{r }
library(dplyr)
library(ggplot2)
v <- table(d6$Q26)
v
```

```{r }

label <- c("I will not buy (-3)",	"Highly Unlikely (-2)",	"Unlikely (-1)",	"Unsure (0)",	"Likely (1)",	"Highly Likely (2)")
num <- c(35, 74, 24, 19, 13 ,10 )
hn <- data.frame(cbind(label,num))
hn
```


```{r echo=FALSE}
 
hn$label <-as.factor(hn$label)
ggplot(hn,aes(label,num))+geom_point(size=3)+geom_line(color='red')+
  labs(title = "How likely are you to buy an energy drink during: Late Night (9pm to Midnight)")

```
 


```{r}
# spending
hg <- table(d5$Q17)
hg
la <- c("I do not drink energy drinks (0)","$0.99 or less (1)","	$1 to $1.99 (2)","	$2 to $2.99 (3)","	$3 to $3.99 (4)","	$4 to 4.99 (5)" )
number <- c(17, 20, 74, 60,  3,  1 )
j <- data.frame(cbind(la,number)) 
j
```
```{r echo=FALSE}
#plot mosaic
spend_perENERGY <- table(j$la,j$number)
mosaicplot(spend_perENERGY)

```

 
 
 
```{r}
a <- table(d5$Q20)
a

pay <- c("I would not buy (0)",	"$0.99 or less (1)",	"$1 to $1.99 (2)",	"$2 to $2.99 (3)",	"$3 to $3.99 (4)",	"$4 to 4.99 (5)",	"$5 or more (6)")

 
amount <- c( 46, 27, 45, 45 , 9  ,3,0 )
f <- data.frame(cbind(pay,amount)) 

f

```



```{r echo=FALSE}
library(ggplot2)
f$pay <-as.factor(f$pay)

ggplot(data=f,aes(x=pay,y=amount))+
  geom_boxplot()+labs(title = " pay for an energy drink that is branded for your specific college if it were organic?")
  

```
```{r }

```



```{r }
library(dplyr)
library(ggplot2)

b <- table(d5$Q17)

pay_sum <- c("$0.99 or less","$1 to $1.99", "$2 to $2.99","$3 to $3.99","c$4 to 4.99" )

#label <- c(0, 1,2,3,4,5 )
amount <- c(17, 20, 74, 60,  3,  1 )d
f <- data.frame(cbind(pay_sum,amount)) 

ggplot(f) +
  geom_bar(aes(x = amount, fill = amount)) +
  xlab("sum") + ylab("Count")

```

```{r }
library(ggplot2)

a <- table(d5$Q18)
a
barplot(a)
#ow much would you be willing to pay for an energy drink that is branded for your specific college?
#d <- c("$0.99 or less (1)",	"$1 to $1.99 (2)",	"$2 to $2.99 (3)",	"$3 to $3.99 (4)","$4 to 4.99 (5)",	"$5 #or more (6)")
 
#y <- c(55, 11, 30, 54, 22,  2,  1 )
#ggplot(data=d5,aes(x=d,y=y))+
 # geom_boxplot()+labs(title = "How often do use facebook")
  
```

 
```{r echo=FALSE}
library(ggplot2)

lda <- c('449$ or less','500-599$','1000-1499$','1500-1999$','>2000$',"jjtu" )
number <- c(13,23, 68, 47, 21,  3)
jh <- data.frame(cbind(lda,number)) 
jh
```





```{r }
library(ggplot2)
c <- table(d5$Q18)
d <- table(d5$Q19)
ld <- c("I would not buy (0)","$0.99 or less (1)",	"$1 to $1.99 (2)",
         "$2 to $2.99 (3)",	"$3 to $3.99 (4)",	"$4 to 4.99 (5)",	"$5 or more (6)" )
q18 <- c(55, 11, 30, 54, 22,  2 , 1)
q19 <- c(23,  5, 14, 31 ,32 ,41, 29 )
jk <- data.frame(cbind(q18,q19)) 
cormat <- round(cor(jk),3)
head(cormat)
 
```





```{r echo=FALSE}
library(reshape2)
melted_cormat <- melt(cormat)
#head(melted_cormat)
library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

  #barplot(a)
```